Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-04-05 Text/Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics.tex
Review (part-1)

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{This paper presents a statistical approach to identify the
underlying roughness characteristics in synthetic aperture radar (SAR)
intensity data. The physical modeling of this kind of data allows to use
the Gamma distribution in the presence of fully-developed speckle, i.e.,
when there are infinitely many independent backscatterers per resolution
cell. This situation is often called ``homogeneous'' or ``textureless''
areas. The \(\mathcal{G}_I^0\) distribution is also a widely accepted
law for heterogeneous and extremely heterogeneous areas. We propose
three test statistics for discriminating between homogeneous and
non-homogeneous areas, i.e., between Gamma and GI0 distributed data,
both with a known number of looks. The first test statistic utilizes a
bootstrapped non-parametric estimator of the Shannon entropy, offering a
robust evaluation in the face of uncertain distributional assumptions.
The second test uses the classic coefficient of variation. The third
test employs an alternative form of estimating the CV based on the ratio
of the mean absolute deviation from the median to the median. We apply
our test statistic to produce maps of \(p\)-values for the hypothesis of
homogeneity. These maps identify different types of targets. We show
that our proposal outperforms its competitors using simulated and SAR
data.}

@@

Synthetic Aperture Radar (SAR) technology has become an important tool
for environmental monitoring and disaster management, providing valuable
imagery in different conditions, including day or night and diverse
weather situations~\cite{Moreira2013,Mu2019}. However, the effective
utilization of SAR data depends on a thorough understanding of its
statistical properties, especially the impact of speckle effects, which
are inherent in SAR data due to the coherent nature of the imaging
process~\cite{Argenti2013}.

In the presence of non-Gaussian speckle interference, SAR data requires
a reliable statistical model for accurate processing. The
\(\mathcal{G}^0\) distribution, suitable for SAR data, includes the
Gamma law as a limit case for fully developed
speckle~\cite{Ferreira2020}, providing flexibility with fewer parameters
for analysis.

Our work is motivated to improve the identification of potential
roughness features in SAR intensity data. Physical modeling of SAR data
allows to take advantage of the gamma distribution in the presence of
fully developed speckle, creating a scenario with an infinite number of
independent backscatterers per unit of resolution, often referred to as
homogeneous areas.

In this context, we present a set of three novel test statistics
designed to discriminate between homogeneous and non-homogeneous areas,
specifically aimed at differentiating between Gamma and
\(\mathcal{G}^0\) distributed data, each with a known number of
appearances. Hence, to understand the core ideas behind our approach, we
explore into the use of properties such as entropy and coefficient of
variation.

The entropy is a fundamental concept in information theory with broad
applications to pattern recognition, statistical physics, stochastic
dynamics, and statistics. Shannon introduced it for a random variable in
1948~\cite{Shannon1948} as a measure of information and uncertainty.\\
In statistics, Shannon entropy is a crucial descriptive parameter,
particularly for assessing data dispersion and conducting tests for
normality, exponentiality, and
uniformity~\cite{Wieczorkowski1999,Zamanzade2012}. Entropy estimation
involves several practical difficulties, especially when the model is
unknown; in these cases, non-parametric methods are used.

Spacing methods have been discussed as a non-parametric approach
in~\cite{AlizadehNoughabi2010,Subhash2021}. This strategy offers
flexibility to address a wide range of models without imposing specific
parametric restrictions.

In our study, entropy serves as the fundamental parameter, providing a
robust assessment by means of a bootstrapped non-parametric estimator of
Shannon entropy.

Simultaneously, we use the classic coefficient of variation (CV) and an
alternative form based on the ratio between the median absolute
deviation and the median. The CV is known as an efficient and robust
index of textural information, measures the homogeneity of the
image~\cite{Lopes1990}.

The CV, introduced by Pearson~\cite{Pearson1896} in 1896, is a relative
measure of dispersion widely used in various areas of applied statistics
including sampling, biostatistics, medical and biological research,
climatology, and other fields
\cite{hendricks1936sampling, Tian2005,SubrahmanyaNairy2003,Chankham2024}.
It facilitates the comparison of variability between different
populations and is especially valuable for comparing variables with
different units. This is because when the main purpose is to compare
variations of several variables, the standard deviation cannot serve as
an adequate measure of variation unless all variables are expressed in
the same unit of measurement and have identical mean values. When these
requirements are not hold for the variables under study, CV is the
relative measure typically used in real applications. The variable with
the highest CV value is the one with the highest relative dispersion
around the mean~\cite{Banik2011}.

Applying these test statistics to generate \(p\)-value maps facilitates
testing of the homogeneity hypothesis, revealing diverse types of
targets within the SAR data. Through extensive experimentation involving
real and simulated SAR data, we demonstrate the superiority of our
proposed methodology over existing approaches.

The article is structured as follows: Section~\ref{sec:Background}
covers statistical modeling and entropy estimation for Intensity SAR
data. Section~\ref{sec:test} outlines hypothesis testing based on
non-parametric entropy estimators and and coefficient of variation. In
Section~\ref{sec:Results}, we present experimental results. Finally, in
Section~\ref{sec:conclusion} conclusions are exhibited.

@@

The primary models used for intensity SAR data include the Gamma and
\(\mathcal{G}_I^0\) distributions~\citep{Frery1997}. The first is
suitable for fully developed speckle and is a limiting case of the
second, which is appealing due to its versatility in accurately
representing regions with various roughness
characteristics~\citep{Cassetti2022}. We denote
\(Z \sim \Gamma_{\text{SAR}}(L, \mu)\) and
\(Z \sim G_I^0(\alpha, \gamma, L)\) to indicate that \(Z\) follows the
distributions characterized by the respective probability density
functions: \begin{align}
    f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gamma1}\\
    f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align} where, in~\eqref{E:gamma1} \(\mu > 0\) is the mean;
in~\eqref{E:gi01} \(\gamma > 0\) is the scale, \(\alpha < -1\) measures
the roughness, \(L \geq 1\) is the number of looks, \(\Gamma(\cdot)\) is
the gamma function, and \(\mathbbm 1_{A}(z)\) is the indicator function
of the set \(A\).

From \eqref{E:gi01}, the \(r\)th moment of \(Z\) is expressed as:
\begin{align}
    E_{G_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\gamma(L)}, \quad \alpha <-r. 
    \label{E:rmom}
\end{align}

Even though the \(\mathcal{G}_I^0\) distribution is defined by the
parameters \(\alpha\) and \(\gamma\), SAR literature commonly utilizes
the texture \(\alpha\) and the mean \(\mu\)~\cite{Nascimento2010}. In
this way, we compute the expected value \(\mu\) using the expression
in~\eqref{E:rmom}, and we reparametrize~\eqref{E:gi01} using \(\mu\),
\(\alpha\), and \(L\). Then \begin{align*}
    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
\end{align*} Thus, the probability density function that characterize
the \(G_I^0(\mu, \alpha, L)\) law is \begin{equation}
        f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big(-\mu(\alpha+1)\big)^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big(-\mu(\alpha+1)+Lz\big)^{L-\alpha}}.\label{E:gi02}
\end{equation}

@@

The parametric representation of Shannon entropy for a system described
by a continuous random variable is: \begin{equation}
  \label{E:entropy2}
  H(Z)=-\int_{-\infty }^\infty \ f(z)\ln f(z)\, \mathrm{d}z,
\end{equation} here, \(f(\cdot)\) is the probability density function
that characterizes the distribution of the real-valued random variable
\(Z\).

Using~\eqref{E:entropy2}, we can express the Shannon entropy of
\(\Gamma_{\text{SAR}}\)in~\eqref{E:gamma1} and \(G_I^0\)
in~\eqref{E:gi02} based on~\cite{Cassetti2022} and~\cite{Ferreira2020}:
\begin{equation}
\label{E:E-gamma}
H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
\end{equation} \begin{multline}
\label{E:E-GIO}
H_{G_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu -\ln\Gamma(L-\alpha)\\
+ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L,
\end{multline} where \(\psi^{(0)}(\cdot)\) is the digamma function.
Figure~\ref{fig:Plot_GI0_to_gamma1}, shows the behaviour of the entropy
of \(G_I^0\) when when
\(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its
convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\)
takes large negative values.

@@

The problem of non-parametric estimating of \(H(Z)\) has been considered
by many authors
including~\cite{vasicek1976test, Wieczorkowski1999,correa1995new,AlOmari2019},
who proposed estimators based on spacings.

One of the earliest non-parametric estimators relying on spacings was
introduced by Vasicek~\cite{vasicek1976test}. Assuming that
\(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) is a random sample from the
distribution \(F(z)\), the estimator is defined as: \begin{equation*}
\label{E:Vas}
    \widehat{H}_{\text{V}}(\bm{Z})=\frac{1}{n}\sum_{i=1}^{n}\ln\left[\frac{n}{2m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
    \end{equation*} where \(m<n/2\) is a positive integer,
\(Z_{(i+m)}-Z_{(i-m)}\) is the \(m\)-spacing and
\(Z_{(1)}\leq Z_{(2)}\leq\ldots\leq Z_{(n)}\) are the order statistics
and \(Z_{(i)}= Z_{(1)}\) if \(i<1\), \(Z_{(i)}= Z_{(n)}\) if \(i>n\).

Several authors have explored adaptations to Vasicek's estimator. We
consider three estimators known for their superior
performance~\cite{Cassetti2022}:

\begin{itemize}
\item
  Correa~\cite{correa1995new}: \(\widehat{H}_{\text{C}}\).
\item
  Ebrahimi et al~\cite{Ebrahimi1994}: \(\widehat{H}_{\mathrm{E}}\).
\item
  Al Omary~\cite{IbrahimAlOmari2014}: \(\widehat{H}_{\mathrm{AO}}\).
\end{itemize}

@@

We employ the bootstrap technique to refine the precision of existing
non-parametric entropy estimators. This approach involves generating new
datasets through resampling with repetition from an existing
one~\cite{Michelucci2021}.

Let's assume that non-parametric entropy estimators
\(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, that is:
\begin{equation}
\label{Eq:bias1}
\operatorname{Bias}\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
\end{equation} Our bootstrap-improved estimators are of the form:
\begin{align*}
\widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
\end{align*} where \(B\) is the number of replications in the bootstrap
technique. Applying this methodology, the original estimators by Correa,
Ebrahimi, and Al-Omari are now denoted as the proposed
bootstrap-enhanced versions: \(\widetilde{H}_{\text{C}}\),
\(\widetilde{H}_{\text{E}}\), and \(\widetilde{H}_{\text{AO}}\),
respectively.

We analyzed the performance of these estimators with a Monte Carlo
study: \(500\) samples of \(G_I^0\) of size
\(n\in\left\{9, 25, 49, 81, 121\right\}\) and several values of the
mean, number of looks and roughness. We present the results with
\(mu\in\left\{1, 10\right\}\), \(\alpha=-10\), and \(L=5\). The results
are consistent for the other situations. In the case of the bootstrap
technique, each sample is replicated \(100\) times with replacement. We
choose to use the following heuristic formula for spacing,
\(m=\left[\sqrt{n}+0.5\right]\).

In Figure~\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and
mean squared error (MSE) between the original non-parametric entropy
estimators and their respective bootstrap-enhanced versions. The use of
the bootstrap technique exhibits more precision, reduced bias and MSE,
and improved convergence. The results of simulation are exhibited in
Table~\ref{tab:table2}.

The precision of estimators, as evidenced by bias and MSE comparisons,
benefits significantly from the bootstrap technique, particularly for
sample sizes below 81.

@@

The population CV is defined as a ratio of the population standard
deviation \((\sigma)\) to the population mean \((\mu)\):

\begin{align}
    \text{CV}=\frac{\sigma}{\mu}, \quad \mu \neq 0.
\end{align}

We explore a robust alternative to the CV as discussed in
\cite{Ospina2019}, involving the ratio of the mean absolute deviation
from the median (MnAD) to the median, two well-known robust measures of
scale and location, respectively. The MnAD is defined as
\(n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|\), where \(\widehat{Q}_2\)
represents an estimate of the population median, which can be
approximated by the sample median.

@@

We aim at testing the following hypotheses:

\[
 \begin{cases}\mathcal{H}_0: \text{ The data comes from the } \Gamma_{\text{SAR}}\\ 
  \mathcal{H}_1:\text{ The data comes from the } G_I^0.\end{cases}
\] In other words, we verify the hypothesis that the data are
fully-developed speckle. The proposed tests are described below.

@@

The first test statistic assess the behavior of the data under the null
hypothesis, through the empirical distribution. \begin{equation}
\label{Eq:test_e}
S_H= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \overline{Z}\right].
\end{equation} The values should be around zero under the null
hypothesis and far otherwise.

Figure~\ref{fig:Plot_density} depicts empirical test statistic densities
for various sample sizes, and Table~\ref{tab:table_stat_combined}
summarizes key statistics, including mean, SD, variance (Var), skewness
(SK), excess kurtosis (EK), and Anderson--Darling \(p\)-values for
normality. Results with \(p\)-values larger than \(0.05\) indicate no
evidence against normality. Small variance and near-zero skewness and
excess kurtosis suggest limited spread, symmetry, and light tails.\\
Normal QQ-plots, confirm that there is no evidence to reject the normal
distribution.

@@

After verifying the normality of the data, we proceeded to explore the
capabilities of the proposed test in terms of size and power. Under
\(\mathcal{H}_0\), the distribution of test statistic is asymptotically
normal. Therefore, the \(p\)-value is calculated as
\(2\Phi(-\mid \varepsilon\mid)\), where \(\Phi\) is the standard
Gaussian cumulative distribution and \(\varepsilon\) is the standardized
test statistic given by: \[
\varepsilon=\frac{\tilde{H}-H_{\Gamma_{\text{SAR}}}}{\hat\sigma}.
\]

We considered nominal levels of \SI{1}{\percent}, \SI{5}{\percent}, and
\SI{10}{\percent}. In reference to the size, \(1000\) simulations have
been used for various sample sizes with satisfactory results. In all
cases, the nominal level has been achieved. The power, in general,
improves with the increase in the sample size and the number of looks.
The results are presented in Table~\ref{tab:table_size_power}.

@@

Similarly, we use another test statistic based on the ratio of the MnAD
to the median. This statistic is given by: \begin{align}
    T_{\text{CV}_{\text{MnAD}}}=\frac{\text{MnAD}}{\text{Median}}.
\end{align} These test statistics allow assessing the variability of the
data.

The situations where the use of CV and \(\text{CV}_{\text{MnAD}}\) may
be appropriate, i.e.~where the observations are positive, the log-normal
(LN) and inverse Gaussian (IG) distribution are often more justified
compared to Gamma and Weibull distributions
\cite{Chaubey2017,takagi1997application}.

The inverse Gaussian distribution is shown to be well approximated by
the log-normal distribution \cite{whitmore1978} which implies that the
IG distribution also does not share the problem of non-existence of
fixed width confidence interval with the Gaussian case.

The LN distribution in two parameters has the following density
function. \begin{align}
    f_Z(z;\mu, \sigma )=\frac{1}{\sigma z\sqrt{2\pi}}\exp\left\{-\frac{(\ln z- \mu)^2}{2\sigma^2}\right\}, \quad z>0, \sigma>0, -\infty < \mu < \infty,
\end{align} here, \(\mu\) is the log-scale parameter and \(\sigma\) is
the shape parameter.

>>>>

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{
This paper presents a statistical approach to identify the underlying roughness properties in synthetic aperture radar (SAR) intensity data. 
The physical modeling of this type of data allows the use of the gamma distribution in the presence of fully developed speckle, i.e. when there are infinitely many independent backscatters per resolution cell. This situation is often referred to as ``homogeneous'' or ``textureless'' regions. 
The \(\mathcal{G}_I^0\) distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions. 
We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e. between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks. 
The first test statistic uses a bootstrapped nonparametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
The second test uses the classical coefficient of variation. 
The third test uses an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median. 
We apply our test statistic to create maps of \(p\) values for the hypothesis of homogeneity. These maps identify different types of targets. 
We show that our proposal outperforms its competitors using simulated and SAR data.}

@@

Synthetic Aperture Radar (SAR) technology has become an important tool for environmental monitoring and disaster management. It provides valuable images under various conditions, including day or night and different weather situations~\cite{Moreira2013,Mu2019}. However, the effective use of SAR data depends on a thorough understanding of its statistical properties, especially the impact of speckle effects inherent in SAR data due to the coherent nature of the imaging process~\cite{Argenti2013}.

In the presence of non-Gaussian speckle interference, SAR data requires a reliable statistical model for accurate processing. The
\(\mathcal{G}^0\) distribution, which is suitable for SAR data, includes the
Gamma law as the limiting case for fully developed speckle~\cite{Ferreira2020} and provides flexibility with fewer parameters for analysis.

Our work aims to improve the identification of potential roughness features in SAR intensity data. Physical modeling of SAR data allows to take advantage of the gamma distribution in the presence of fully developed speckles and to create a scenario with an infinite number of independent backscatterers per resolution unit, often referred to as homogeneous regions.

In this context, we present a set of three novel test statistics that aim to distinguish between homogeneous and non-homogeneous domains, in particular between gamma and
\(\mathcal{G}^0\) distributed data, each with a known number of looks. To understand the core ideas behind our approach, we explore the use of properties such as entropy and coefficient of variation.

Entropy is a fundamental concept in information theory with far-reaching applications in pattern recognition, statistical physics, stochastic dynamics and statistics. Shannon introduced it in 1948~\cite{Shannon1948} for a random variable as a measure of information and uncertainty.\\
In statistics, Shannon entropy is a crucial descriptive parameter, especially for evaluating data dispersion and performing tests for normality, exponentiality and uniformity~\cite{Wieczorkowski1999,Zamanzade2012}. Entropy estimation is associated with some practical difficulties, especially when the model is unknown. In these cases, non-parametric methods are used.
Spacing methods have been discussed as a non-parametric approach in~\cite{AlizadehNoughabi2010,Subhash2021}. This strategy provides the flexibility to consider a wide range of models without enforcing certain parametric constraints.

The coefficient of variation (CV), introduced in 1896 by Pearson~\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields
\cite{hendricks1936sampling, Tian2005,SubrahmanyaNairy2003,Chankham2024}.
It facilitates the comparison of variability between different populations and is particularly valuable for comparing variables with different units. This is because when the main purpose is to compare the variations of several variables, the standard deviation can only serve as an adequate measure of variation if all variables are expressed in the same unit of measurement and have identical means. If these conditions are not met for the variables under investigation, the CV is the relative measure that is usually used in real applications. The variable with the highest CV value is the one with the largest relative dispersion around the mean value~\cite{Banik2011}.

In our study, entropy serves as a fundamental parameter that allows a robust evaluation using a bootstrapped nonparametric estimator of the
Shannon entropy.
At the same time, we use the classical CV and an alternative form based on the ratio between the median absolute deviation and the median. 
The CV is known as an efficient and robust index for texture information and measures the homogeneity of the image~\cite{Lopes1990}.
Applying these test statistics to generate maps of \(p\) values facilitates testing the homogeneity hypothesis and reveals different types of targets in the SAR data. 
Through extensive experiments with real and simulated SAR data, we demonstrate the superiority of our proposed method over existing approaches.

The article is structured as follows: Section~\ref{sec:Background}
deals with statistical modeling and entropy estimation for intensity SAR
data. Section~\ref{sec:test} outlines hypothesis tests based on nonparametric entropy estimators and coefficients of variation. In
Section~\ref{sec:Results} we present experimental results. Finally, in
Section~\ref{sec:conclusion} the conclusions are presented.

@@

The primary models used for SAR intensity data include the gamma and the
\(\mathcal{G}_I^0\) distributions~\citep{Frery1997}. The first model is suitable for fully developed speckle and is a limiting case of the second model, which is interesting due to its versatility in accurately representing regions with different roughness properties~\citep{Cassetti2022}.
We denote
\(Z \sim \Gamma_{\text{SAR}}(L, \mu)\) and
\(Z \sim G_I^0(\alpha, \gamma, L)\) to indicate that \(Z\) follows the
distributions characterized by the respective probability density
functions (pdfs): 
\begin{align}
    f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z)\label{E:gamma1}\\
    \intertext{ and }
    f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align} 
where \(\mu > 0\) is the mean, \(\gamma > 0\) is the scale, \(\alpha < -1\) measures
the roughness, \(L \geq 1\) is the number of looks, \(\Gamma(\cdot)\) is
the gamma function, and \(\mathbbm 1_{A}(z)\) is the indicator function
of the set \(A\).

If we take the law with the density~\eqref{E:gi01}, the \(r\)th non-central moment of \(Z\) is expressed as follows:
\begin{align}
    E_{G_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, \quad \alpha <-r. 
    \label{E:rmom}
\end{align}

Although the \(\mathcal{G}_I^0\) distribution is defined by the parameters \(\alpha\) and \(\gamma\), in the SAR literature~\cite{Nascimento2010} the texture \(\alpha\) and the mean \(\mu\) are usually used. In this way, we calculate the expected value \(\mu\) using the expression in~\eqref{E:rmom}, and we reparametrize~\eqref{E:gi01} with \(\mu\),
\(\alpha\), and \(L\).
Then \begin{align*}
    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
\end{align*} 
The reparametrized pdf that characterizes the law \(G_I^0(\mu, \alpha, L)\) is thus
\begin{equation}
        f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}.\label{E:gi02}
\end{equation}

@@

The parametric representation of the Shannon entropy for a system described by a continuous random variable is:
\begin{equation}
  \label{E:entropy2}
  H(Z)=-\int_{-\infty }^\infty \ f(z)\ln f(z)\, \mathrm{d}z,
\end{equation} 
here, \(f(\cdot)\) is the pdf
that characterizes the distribution of the real-valued random variable
\(Z\).

Using~\eqref{E:entropy2}, we can express the Shannon entropy of
\(\Gamma_{\text{SAR}}\)in~\eqref{E:gamma1} and \(G_I^0\)
in~\eqref{E:gi02} based on~\cite{Cassetti2022} and~\cite{Ferreira2020}:
\begin{equation}
\label{E:E-gamma}
H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
\end{equation} \begin{multline}
\label{E:E-GIO}
H_{G_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu -\ln\Gamma(L-\alpha)\\
+ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L,
\end{multline} where \(\psi^{(0)}(\cdot)\) is the digamma function.
Figure~\ref{fig:Plot_GI0_to_gamma1}, shows the behavior of the entropy of \(G_I^0\) when
\(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), where the approximation to the entropy of \(\Gamma_{\text{SAR}}\) can be observed when \(\alpha\)
assumes large negative values.
In an interpretative sense, we can conclude that the more heterogeneous (high values of $\alpha$) the SAR region is, the higher the value of entropy (or degree of disorder).
It is worth noting that this conclusion confirms what is written in the SAR literature.

@@

The problem of non-parametric estimation of \(H(Z)\) has been considered by many authors, including~\cite{vasicek1976test, Wieczorkowski1999,correa1995new,AlOmari2019},
who have proposed estimators based on spacings.

One of the first non-parametric estimators based on spacings was introduced by Vasicek~\cite{vasicek1976test}. Under the assumption that
\(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) is a random sample from the distribution \(F(z)\), the estimator is defined as:
\begin{equation*}
\label{E:Vas}
    \widehat{H}_{\text{V}}(\bm{Z})=\frac{1}{n}\sum_{i=1}^{n}\ln\left[\frac{n}{2m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
    \end{equation*} where \(m<n/2\) is a positive integer,
\(Z_{(i+m)}-Z_{(i-m)}\) is the \(m\)-spacing and
\(Z_{(1)}\leq Z_{(2)}\leq\ldots\leq Z_{(n)}\) are the order statistics
and \(Z_{(i)}= Z_{(1)}\) if \(i<1\), \(Z_{(i)}= Z_{(n)}\) if \(i>n\).

Several authors have explored adaptations to Vasicek's estimator. 
We consider three estimators known for their superior performance~\cite{Cassetti2022}:
Correa~\cite{correa1995new}, \(\widehat{H}_{\text{C}}\);
Ebrahimi et al~\cite{Ebrahimi1994}, \(\widehat{H}_{\mathrm{E}}\);
and Al Omary~\cite{IbrahimAlOmari2014}, \(\widehat{H}_{\mathrm{AO}}\).

@@

We use the bootstrap technique to refine the accuracy of existing nonparametric entropy estimators. In this approach, new data sets are generated by replicate sampling from an existing data set~\cite{Michelucci2021}.

Let us assume that non-parametric entropy estimators
\(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, i.e:\begin{equation}
\label{Eq:bias1}
\operatorname{Bias}\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
\end{equation} Our bootstrap-improved estimators are of the form:
\begin{align*}
\widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
\end{align*} 
where \(B\) is the number of replications in the bootstrap
technique. 
Applying this methodology, the original estimators of Correa,
Ebrahimi and Al-Omari are now referred to as the proposed bootstrap-enhanced versions:
\(\widetilde{H}_{\text{C}}\),
\(\widetilde{H}_{\text{E}}\), and \(\widetilde{H}_{\text{AO}}\),
respectively.

We analyzed the performance of these estimators with a Monte Carlo study: \(500\) samples of \(G_I^0\) of size
\(n\in\left\{9, 25, 49, 81, 121\right\}\) and different values for mean, number of looks and roughness. We present the results with
\(\mu\in\left\{1, 10\right\}\), \(\alpha=-10\) and \(L=5\). The results are also adherent for the other situations. In the bootstrap technique, each sample is replicated a hundred times with replacement. We use the following heuristic formula for spacing,
\(m=\left[\sqrt{n}+0.5\right]\).

In Figure~\ref{fig:Plot_bias_mse_gi0} we show comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions. The use of the bootstrap technique shows higher precision, lower bias and MSE, and improved convergence. The results of the simulation can be found in
Table~\ref{tab:table2}.

The precision of the estimators resulting from the comparison of bias and MSE benefits significantly from the bootstrap technique, especially for sample sizes below 81.

@@

The population CV is defined as the ratio of the population standard deviation \((\sigma)\) to the population mean \((\mu)\):

\begin{align}
    \text{CV}=\frac{\sigma}{\mu}, \quad \text{ for }\mu \neq 0.
\end{align}

We explore a robust alternative to CV, as described in
\cite{Ospina2019}, which incorporates the ratio between the mean absolute deviation from the median (MnAD) and the median, two well-known robust measures of
scale and location, respectively. The sample version for the MnAD is defined as
\(n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|\), where \(\widehat{Q}_2\)
is an estimate for the median of the population, which can be approximated by the median of the sample.

@@

We aim at testing the following hypotheses:
\[
 \begin{cases}\mathcal{H}_0: \text{ The data comes from the } \Gamma_{\text{SAR}}\\ 
  \mathcal{H}_1:\text{ The data comes from the } G_I^0.\end{cases}
\] 
In the physical sense, we are testing the hypothesis that the data are fully developed speckle.
As for the parametric problem, once it is not possible to define the hypothesis $\mathcal{H}_0=\alpha=-\infty$, it is impossible to solve this problem with the parametric statistical inference alternatives (such as likelihood ratio, score, grandient and Wald hypothesis test).
The proposed tests to solve this physical problem in SAR systems are described below.

@@

The first test statistic evaluates the behavior of the data under the null hypothesis using the empirical distribution: 
\begin{equation}\label{Eq:test_e}
S_H= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \overline{Z}\right].
\end{equation} 
The values should be zero under the null hypothesis and otherwise far from it.

Figure~\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes, and Table~\ref{tab:table_stat_combined}
summarizes the main descriptive statistics, including mean, SD, variance (Var), skewness
(SK), excessive kurtosis (EK) and Anderson--Darling \(p\) values for normality. Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption. A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, symmetry and a slight tail.\\
Normal QQ plots confirm that there is no evidence against a normal distribution.

@@

After checking the normality of the data, we examined the possibilities of the proposed test in terms of size and power.
Under \(\mathcal{H}_0\), the distribution of the test statistic is asymptotically normal.
Therefore, the \(p\) value is calculated as
\(2\Phi(-\mid \varepsilon\mid)\), where \(\Phi\) is the standard
Gaussian cumulative distribution and \(\varepsilon\) is the standardized test statistic given by :
\[
\varepsilon=\frac{\tilde{H}-H_{\Gamma_{\text{SAR}}}}{\hat\sigma}.
\]

We have nominal levels of \SI{1}{\ percent}, \SI{5}{\ percent}, and
\SI{10}{\percent}. 
In terms of size, \(1000\) simulations were used for different sample sizes with satisfactory results. 
In all cases, the nominal level was achieved. 
The power generally improves with increasing sample size and number of looks.
The results are shown in Table~\ref{tab:table_size_power}.

@@

Similarly, we use another test statistic based on the ratio between the MnAD and the median.
This statistic is given by:
\begin{align}
    T_{\text{CV}_{\text{MnAD}}}=\frac{\text{MnAD}}{\text{Median}}.
\end{align} These test statistics allow assessing the variability of the
data.

The situations in which the use of CV and \(\text{CV}_{\text{MnAD}}\) may be appropriate, i.e.~when the observations are positive, the log-normal
(LN) and the inverse Gaussian distribution (IG) are often more appropriate than the Gamma and Weibull distributions
\cite{Chaubey2017,takagi1997application}.

It is shown that the IG distribution is well approximated by the log-normal distribution, which means that the
IG distribution also does not share the problem of the non-existence of a fixed-width confidence interval with the Gaussian case \cite{whitmore1978}.

The LN distribution in two parameters has the following density
function. 
\begin{align}
    f_Z(z;\mu_{\text{LN}}, \sigma )=\frac{1}{\sigma z\sqrt{2\pi}}\exp\left\{-\frac{(\ln z- \mu_{\text{LN}})^2}{2\sigma^2}\right\}\mathbbm 1_{\mathbbm R_+}(z),
\end{align} here, $\sigma>0$, $-\infty < \mu_{\text{LN}} < \infty$, \(\mu\) is the log-scale parameter and \(\sigma\) is
the shape parameter.

\vskip+1ex
{\color{red} ADCN: Fiz uma diferen\c{c}a entre as nota\c{c}\~oes para m\'edia da G0I e da LN. Por favor, verifique se faz sentido, isto \'e se ela n\~ao \'e encaixada a G0I neste contexto.}
\vskip+1ex
